---
title: "chess"
author: "Yadu"
date: "February 13, 2016"
output: html_document
---

Download the file first and then read the txt file into R.

```{r}
library(RCurl)
library(stringr)
url = "https://github.com/cyadusha/tournamentinfo/blob/master/tournamentinfo.txt"
x = getURL(url)
tournamentinfo = read.delim(file = textConnection(x), header = TRUE)
```

```{r}
nrow(tournamentinfo)
```

We know that we desire a sequence that has a length of 64 values. The txt file that is inputted into R has 195 rows. This does not imply that there are 195 players. Therefore, we input the following command in order for us to know which rows should be subsetted from the data. 

```{r}
subsetrows = c(seq(from = 4, to = 193, by = 3))
subsetrows
```

This is where we obtain the player names, total points, and the opponents' identifications.

```{r}
t1 = tournamentinfo[c(subsetrows[1:64]), ]
names = str_trim(unlist(str_extract(t1, "[[:alpha:]]+ ?[[:alpha:]]+ [[:alpha:]]+")))
totalpoints = str_trim(unlist(str_extract(t1, "[[:digit:]].[[:digit:]]")))
location = str_locate(t1[1], "39|W")
opponents = str_sub(t1, location[1])
opponents = unlist(str_replace_all(opponents, "[:alpha:]+", ""))
opponents = unlist(str_replace_all(opponents, "[:space:]+", ""))
opponents = str_sub(opponents, 1, -2)
opponents = unlist(str_split(opponents, "[|]"))
opponents = c(as.numeric(unlist(str_extract(opponents, "[[:digit:]]+"))))
```

The rows where the state names and the preratings are stored are one row below those of the player's names. 

```{r}
subsetrows2 = subsetrows + 1
subsetrows2
```

This is where we obtain the state names and the preratings. 

```{r}
t2 = tournamentinfo[c(subsetrows2[1:64]), ] 
states = str_trim(unlist(str_extract(t2, "[:alpha:]+[:alpha:]")))
prerating = str_trim(unlist(str_extract(t2, "R: ?.[[:digit:]]{3}|R: ?.[[:digit:]]{4}")))
prerating = str_sub(prerating, start = 4, end = 7)
prerating = as.numeric(prerating)
prerating = data.frame(prerating)
```

We have to set up the identification numbers of the opponents as numeric values. 

```{r}
opponents = data.frame(matrix(as.numeric(opponents), nrow = 64, ncol = 7, byrow = T))
```

Next, we match the identification number of each opponent given in each round with the prerating of the opponent given in the row below the name.

```{r}
opponents1 = data.frame(V1 = prerating$prerating[opponents$X1])
opponents2 = data.frame(V2 = prerating$prerating[opponents$X2])
opponents3 = data.frame(V3 = prerating$prerating[opponents$X3])
opponents4 = data.frame(V4 = prerating$prerating[opponents$X4])
opponents5 = data.frame(V5 = prerating$prerating[opponents$X5])
opponents6 = data.frame(V6 = prerating$prerating[opponents$X6])
opponents7 = data.frame(V7 = prerating$prerating[opponents$X7])
opponents = data.frame(opponents1, opponents2, opponents3, opponents4, opponents5, opponents6, opponents7)
```

Finally we compute the average opponent rating for each player. For some players, the value in some of their rounds is actually null. For those players we will just average the given values. 

```{r}
averageopponentrating = round(rowMeans(opponents, na.rm = T), 0)
```

We collect all of the columns computed above into a single data frame of 5 columns and 64 rows.

```{r}
tournamentdata = data.frame(names, states, totalpoints, prerating, averageopponentrating)
colnames(tournamentdata) = c("Name", "State", "Total Number of Points", "Pre-Rating", "Average Pre-Rating of Opponents")
```

Now we write the data into a .csv file.

```{r}
write.table(tournamentdata, file = "tournamentdata.csv", sep = ",", row.names = FALSE)
```

Now we make sure the data was read into a .csv file. 

```{r}
tournamentdata = read.csv(file = "/Users/chittampalliyashaswini/Desktop/Yadu/tournamentdata.csv", sep = ",", header = TRUE)
```